### 2009-07-09 docs/architecture/architecture.tex
define the acronym AMR change mk_spong_2d --> example_2d for consistency
stuff for the far future

MAESTRO's gridding is handled by the boxlib library.  The underlying
idea in boxlib is to allow for adaptive mesh refinement.  The domain
is broken into boxes.  At the coarsest (base) level of refinement, the
entire computational domain is covered, either by one box or broken
across many boxes.  Higher levels of refinement have finer zones
(typically $2\times$).  Only a portion of the domain may be covered by
the higher levels of refinement.  \MarginPar{Nesting?}
For parallel computations, the boxes are spread across processors, in
a fashion designed to put roughly equal amounts of work on each
processor (load balancing).

@@

\begin{figure}[h]
\centering
\includegraphics[width=4.0in]{\archfigpath/index_grid2}
\caption{\label{fig:boxes} Three boxes that comprise a single level.
At this resolution, the domain is 20$\times$18 zones.}
\end{figure}

@@

\begin{verbatim}
          select case (dm)
          case (2)
             call example_2d(sp(:,:,1,rho_comp),ng_sp,lo,hi,dx(n,:),dt)
          case (3)
             call example_3d(sp(:,:,:,rho_comp),ng_sp,lo,hi,dx(n,:),dt)
          end select
       end do

    end do

@@

          ! operate on density(i,j)

       enddo
    end do

  end subroutine mk_sponge_2d
\end{verbatim}

@@

@@

>>>>

MAESTRO's gridding is handled by the boxlib library.  The underlying
idea in boxlib is to allow for adaptive mesh refinement---different
regions of the domain can have different spatial resolutions.  The
domain is broken into boxes.  At the coarsest (base) level of
refinement, the entire computational domain is covered, either by one
box or broken across many boxes.  Higher levels of refinement have
finer zones (typically $2\times$).  Only a portion of the domain may
be covered by the higher levels of refinement.  \MarginPar{Nesting?}
For parallel computations, the boxes are spread across processors, in
a fashion designed to put roughly equal amounts of work on each
processor (load balancing).

@@

\begin{figure}[h]
\centering
\includegraphics[width=4.0in]{\archfigpath/index_grid2}
\caption{\label{fig:boxes} Three boxes that comprise a single level.
At this resolution, the domain is 20$\times$18 zones.  Note that the
indexing in boxlib starts with $0$.}
\end{figure}

@@

\begin{verbatim}
          select case (dm)
          case (2)
             call example_2d(sp(:,:,1,rho_comp),ng_sp,lo,hi,dx(n,:),dt)
          case (3)
             call example_3d(sp(:,:,:,rho_comp),ng_sp,lo,hi,dx(n,:),dt)
          end select
       enddo    ! end loop over boxes

    enddo    ! end loop over levels

@@

          ! operate on density(i,j)
          ! ...

       enddo
    enddo

  end subroutine example_2d
\end{verbatim}

@@

\section{Multigrid}

\section{MAESTRO Modules}

\subsection{{\tt fill\_3d\_module}}

\subsection{{\tt geometry}}

\subsection{{\tt variables}}

@@

\subsection{Plane-Parallel Geometry}

\subsection{Full Star / Spherical}

\subsection{Small-scale Flame}
